Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
temporarily disabled hyperlinks

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}

@@

\newcommand{\system}{\textsc{DreamHacker}~}
\newcommand{\lowerBound}{\mathscr{L}}
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{listings}
\usepackage{amsthm}
% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfig} 
\usepackage{fancyvrb}

@@

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

@@

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
complicated by the fact that the programs are unobserved latent variables,
and so we must solve a difficult search problem to find any programs at all. To make
inference tractable our model learns a bottom-up \emph{recognition
  model} alongside the top-down generative model
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs.  The neural network $q$ implements an amortized
inference/compiled inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model by speeding up the search for programs.

>>>>

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
%\usepackage{hyperref}

@@

\newcommand{\system}{\textsc{DreamHacker}~}
\newcommand{\lowerBound}{\mathscr{L}}
% Use the following line for the initial blind version submitted for review:
\usepackage[nohyperref]{icml2018}

%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{listings}
\usepackage{amsthm}
% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfig} 
\usepackage{fancyvrb}

@@

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}

\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

@@

Inference in the generative model in Figure~\ref{graphicalModel}(a) is
complicated by the fact that the programs are unobserved,
and so we must solve a difficult search problem to find any programs at all. To make
search tractable we learn a bottom-up \emph{recognition
  model} alongside the top-down generative model
(Figure~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs.  The neural network $q$ implements an amortized
inference/compiled inference
scheme~\cite{le2016inference,ritchie2016deep} for the generative
model by speeding up the search for programs.
